\appendix
\section{Glossary}\label{_glossary}

\subsection*{A}
\subsubsection*{AJAX}
It's a set of web development techniques using many web technologies on the client-side to create asynchronous web applications.

\subsubsection*{Amazon S3}
Amazon S3 or Amazon Simple Storage Service is a service offered by Amazon Web Services that provides object storage through 
a web service interface.

\subsubsection*{Amazon Web Services}
Amazon Web Services is a subsidiary of Amazon providing on-demand cloud computing platforms 
and APIs to individuals, companies, and governments, on a metered pay-as-you-go basis.

\subsubsection*{API}
Acronym for Application Programming Interface. Indicates a set of procedures
(generally grouped by specific tools) suitable for carrying out a given task. Often this term
represents the software libraries of a programming language.

\subsubsection*{Azure}
It's a cloud computing service created by Microsoft for building, testing, deploying, and managing 
applications and services through Microsoft-managed data centers.

\subsection*{B}
\subsubsection*{Babel}
It's a free and open-source JavaScript transcompiler.

\subsection*{C}
\subsubsection*{CI}
In software engineering, continuous integration is the practice of merging all developers' working 
copies to a shared mainline several times a day.

\subsubsection*{CRUD}
In computer programming, create, read, update, and delete is a software architectural style 
regarding the four basic operations of persistent storage.

\subsection*{D}
\subsubsection*{DOM}
Acronym for Document Object Model. is a cross-platform and language-independent interface that 
treats an XML or HTML document as a tree structure wherein each node is an object representing 
a part of the document.


\subsection*{E}

\subsection*{EML-FE}
\textit{EmporioLambda Front-End:} service for the front-end mentioned in the C2 specification.

\subsection*{EML-BE}
\textit{EmporioLambda Back-End:} service for the back-end part of the C2 specification.

\subsubsection*{EsLint}
Static code analysis tool to identify problematic patterns found in \glock{TypeScript}
code.

\subsection*{G}
\subsubsection*{ Github Actions}
It's a hosted continuous integration service used to build and test software projects hosted on GitHub.


\subsection*{J}
\subsubsection*{Jest}
It's a JavaScript testing framework.


\subsubsection*{JWT}
JSON Web Token is an Internet proposed standard for creating data with optional signature 
and/or optional encryption whose payload holds JSON that asserts some number of claims.

\subsection*{M}
\subsection*{Microservice}
Microservice architecture arranges an application as a collection of loosely coupled services.

\subsubsection*{Mock}
In object-oriented programming, mock objects are simulated objects that mimic the behavior 
of real objects in controlled ways, most often as part of a software testing initiative.

\subsection*{N}
\subsubsection*{NoSQL}
A NoSQL database provides a mechanism for storage and retrieval of data that is modeled 
in means other than the tabular relations used in relational databases.

\subsection*{R}
\subsubsection*{Redux}
It's an open-source JavaScript library for managing application state.

\subsubsection*{RESTful}
Representational state transfer is a software architectural style which uses a subset of HTTP. 
It is commonly used to create interactive applications that use Web services. 
A Web service that follows these guidelines is called RESTful.

\subsection*{S}
\subsubsection*{Swagger}
It's an Interface Description Language for describing RESTful APIs expressed using JSON.

\subsubsection*{Serverless}
Serverless computing is a cloud computing execution model in which the cloud provider allocates 
machine resources on demand, taking care of the servers on behalf of their customers.

\subsection*{V}
\subsubsection*{V8}
It's an open-source JavaScript.

\subsection*{X}
\subsubsection*{XML}
Acronym for Extensible Markup Language. It's a markup language that defines a set of rules for encoding documents.
